Autonomous Oceanographic Sampling Designs using Excursion Sets for Multivariate Gaussian random fields

### 2020-06-04 main_new.tex
updates

In this section, we calculate EPs and the Bernoulli variance for a few bivariate
Gaussian distributions to illustrate the concepts articulated above.
Fig. \ref{illus_bivarDens} shows contour plots of three different
densities with increasing correlation $\gamma$ between temperature and
salinity.
\begin{figure}[h!] \centering
  \includegraphics[width=0.99\textwidth]{Figures/illus_bivar.pdf}
  \caption{Density contour plots with different correlations between
    temperature and salinity. The densities have unit variance and the
    thresholds are identical to the mean values $5^o C$ and
    $30 mg/l$. X-axis is temperature and y-axis is salinity.}
\label{illus_bivarDens}
\end{figure}
Here, the thresholds are set equal to the mean $\mu_1=t_1=5^o C$, and
salinity $\mu_2=t_2=30$ mg/l, and the EP is $p=P(Z_1 < 5,Z_2 < 30)$. The displayed densities have unit
standard deviations for both temperature and salinity, but we also
study the effect of doubling the standard deviations.

>>>>

% In this section, 
We calculate EPs and the Bernoulli variance for a few bivariate
Gaussian distributions to illustrate the concepts articulated above.
Fig. \ref{illus_bivarDens} shows contour plots of three different
densities with increasing correlation $\gamma$ between temperature and
salinity. \kc{What is the source of this data?}
\begin{figure}[h!] \centering
  \includegraphics[width=0.99\textwidth]{Figures/illus_bivar.pdf}
  \caption{Density contour plots with different correlations between
    temperature and salinity. The densities have unit variance and the
    thresholds are identical to the mean values $5^o C$ and
    $30 mg/l$. X-axis is temperature and y-axis is salinity.}
\label{illus_bivarDens}
\end{figure}
Here, the thresholds are set equal to the mean $\mu_1=t_1=5^o C$, and
salinity $\mu_2=t_2=30$ mg/l, and the EP is $p=P(Z_1 < 5,Z_2 < 30)$.
The displayed densities have unit standard deviations for both
temperature and salinity, but we also study the effect of doubling the
standard deviations.
